Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE)

### 2014-02-04 WSSSPE1_report/WSSSPE1_summary_report.tex
a note and some corrections

He experienced problems with staff retention with respect to private organizations which reward 
those combining research and software expertise (the ``Google Bus''). However,
he is a strong fan of private sector sustainability sources and PPP. He
noted that making a successful business from scientific software alone
is very rare: founders overvalue while customers undervalue. He noted
that to last, an open source project needs a minimal funding requirement
even with a vibrant community -- good will only goes so far if you are
being paid to do something else.

@@

His talk used an example from data reduction in Astronomy, where he
needed to remove interfering effects from the device. He built a
``bad pixel mask'', and realized though while this is persistent, there
was no way/practice of sharing this with the data, so many researchers
repeated the same calculations. He estimated that 13 wasted person-years were wasted in
this redundant calculation.

>>>>

He experienced problems with staff retention with respect to private organizations which reward 
those combining research and software expertise (the ``Google Bus''). However,
he is a strong fan of private sector sustainability sources and PPP\note{what does PPP mean?}. He
noted that making a successful business from scientific software alone
is very rare: founders overvalue while customers undervalue. He noted
that to last, an open source project needs a minimal funding requirement
even with a vibrant community -- good will only goes so far if you are
being paid to do something else.

@@

His talk used an example from data reduction in Astronomy, where he
needed to remove interfering effects from the device. He built a
``bad pixel mask'', and realized that while this is persistent, there
was no way/practice of sharing this with the data, so many researchers
repeated the same calculations. He estimated that 13 person-years were wasted in
this redundant calculation.
